\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The work was supported by the Minister of Science and Technology of Taiwan project 106-2221-E-001-009-MY3 and Czech Science Foundation project 17-12465S.}

### 2019-08-26 draft.tex
Added authors and Czech acknowledgement
final version

%\usepackage{latexsym}
\usepackage{setspace}
\usepackage{cancel}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage{amssymb}
%\usepackage{times}

@@

\title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
work was supported by the Czech Science Foundation project
17-12465S.}\vspace*{-2mm}}

@@

\vspace*{-4mm}\begin{abstract} The MapReduce framework for data-parallel
computation was first proposed by Google~\cite{dean04} and later implemented in
the Apache Hadoop project. Under the MapReduce framework, a reducer computes
output values from a sequence of input values transmitted over the network. Due
to non-determinism in data transmission, the order in which input values arrive
at the reducer is not fixed. In relation to this, the \emph{commutativity
problem} of reducers asks if the output of a reducer is independent of the order
of its inputs. Indeed, there are several advantages for a reducer to be
commutative, e.g., the verification problem of a MapReduce program can be
reduced to the problem of verifying a sequential program. We present the tool
J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective
heuristics for reducer commutativity analysis. J-ReCoVer is the first tool that
is specialized in checking reducer commutativity. Our experimental results over
118 benchmark examples collected from open repositories are very positive;
J-ReCoVer correctly handles over 97~\% of them. \end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-5mm}\section{Introduction}\label{section:introduction}\vspace*{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%!!!!!!!!!!!!!!!!!!!!!!!!
\enlargethispage{5mm}
%!!!!!!!!!!!!!!!!!!!!!!!!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-2mm} \section{Notations and Definitions}
\label{section:integer-reducers} \vspace*{-1mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-2mm}
\section{Overview of the J-ReCoVer Tool} \label{sec:overview}
\vspace*{-1mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{wrapfigure}{r}{7cm}
	\vspace{-8mm}
\centering
	\scalebox{0.7}{
		\begin{tikzpicture}

@@

		\end{tikzpicture}
	}
		\vspace{-1cm}
	\caption{Overview of the J-ReCoVer tool. }\label{fig:overview-jrecover}
		\vspace{-0.8cm}

@@

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\enlargethispage{4mm}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-2mm}
\section{The Preprocessor and the Prover} \label{sec:preprocessor_prover}
\vspace*{-1mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%=============================================================================
\vspace*{-2mm}
\subsection{The Program Transformation in the Preprocessor}
\label{sec:program_trans1}
\vspace*{-1mm}
%=============================================================================

%-----------------------------------------------------------------------------
%\paragraph*{Handling the access to $\cur$ before entering the loop.}
%-----------------------------------------------------------------------------

\begin{wrapfigure}[11]{r}{3.5cm}
	\vspace{-18mm}
	\begin{algorithm}[H]
		\;\;$m := \cur + 10$; \;
		\Loop{}{
			$t:=\cur$\;
			\uIf{ $t> m$}{
				$m := t$ \;
			}
		};
		$out(m)$\;\;
	\end{algorithm}
	\vspace{-0.8cm}
	\caption{The max$^+$ reducer with input before the main loop.}
	\vspace{-11mm}
	\label{fig:reducer_max1}
\end{wrapfigure}

%	\begin{figure}[t]
%		\begin{minipage}{0.4\textwidth}
%			\begin{algorithm}[H]
%				\;\;$m := \cur + 10$; \;
%				\Loop{}{
%					$t:=\cur$\;
%					\uIf{ $t> m$}{
%						$m := t$ \;
%					}
%				};
%				$out(m)$\;\;
%			\end{algorithm}
%			\caption*{(a) Reducer max$^+$}
%		\end{minipage}
%		\begin{minipage}{0.6\textwidth}
%			\begin{algorithm}[H]
%				$s:=*;$\;
%				\Loop{}{
%					\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
%					\uElse{
%						$t:=\cur$\;
%						\uIf{ $t > m$}{
%							$m := t$ \;
%						}
%					}
%				};
%				$out(m)$
%			\end{algorithm}
%			\caption*{(b) Reducer max$^{+\mathtt{fix}}$}
%		\end{minipage}
%		\caption{Reducer examples}
%		\label{fig:reducer_max}
%	\end{figure}

@@

@@

\begin{wrapfigure}[12]{r}{5.3cm}
	\vspace{-10mm}
	\begin{algorithm}[H]
		$s:=1;$\;
		\Loop{}{
			\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
			\uElse{
				$t:=\cur$\;
				\uIf{ $t > m$}{
					$m := t$ \;
				}
			}
		};
		$out(m)$
	\end{algorithm}	
	\vspace{-2mm}
	\caption{The max$^{+\mathtt{fix}}$ reducer.}
	\vspace{-4mm}
	\label{fig:reducer_max2}
\end{wrapfigure}

@@

%=============================================================================
\vspace{-2mm}
\subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
\vspace{-2mm}
\label{sec:prover}
%=============================================================================

@@

The command $s_2$
can be viewed as a function $F$ that reads the values of all variables and the
current input before executing $s_2$ and outputs the values of all variables
after $s_2$. Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1}
\rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$ where $n$ is
the current input value of the reducer, $x_i$ and $x_i'$ are the values of the
variables before and after the execution of $s_2$, respectively, for
$i\in[1,k]$. The construction of $F$ from $s_2$ can be done in the standard way.

@@

%=============================================================================
\vspace{-2mm}
\subsection{An Optimisation by Live Variable Analysis}
\vspace{-2mm}
\label{section:optimizations}
%=============================================================================

@@

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\enlargethispage*{4mm}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

\begin{wraptable}[7]{r}{40mm}
	\vspace{-8mm}
	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}

@@

%-----------------------------------------------------------------------------
\vspace{-1mm}
\paragraph*{Benchmark collection} 
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
\vspace{-1mm}
\paragraph*{Results} 
%-----------------------------------------------------------------------------

@@

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\enlargethispage*{4mm}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\bibliographystyle{splncs-sorted}
\bibliography{refs}

\input{appendix}

>>>>

%\usepackage{latexsym}
\usepackage{setspace}
\usepackage{cancel}
\usepackage{graphicx}
\usepackage{amssymb}
%\usepackage{times}

@@

\title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
work was supported by the Minister of Science and Technology of Taiwan project 106-2221-E-001-009-MY3 and Czech Science Foundation project
17-12465S.}}

@@

\begin{abstract} The MapReduce framework for data-parallel
computation was first proposed by Google~\cite{dean04} and later implemented in
the Apache Hadoop project. Under the MapReduce framework, a reducer computes
output values from a sequence of input values transmitted over the network. Due
to non-determinism in data transmission, the order in which input values arrive
at the reducer is not fixed. In relation to this, the \emph{commutativity
problem} of reducers asks if the output of a reducer is independent of the order
of its inputs. Indeed, there are several advantages for a reducer to be
commutative, e.g., the verification problem of a MapReduce program can be
reduced to the problem of verifying a sequential program. We present the tool
J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective
heuristics for reducer commutativity analysis. J-ReCoVer is the first tool that
is specialized in checking reducer commutativity. Our experimental results over
118 benchmark examples collected from open repositories are very positive;
J-ReCoVer correctly handles over 97~\% of them. \end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{section:introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Notations and Definitions}
\label{section:integer-reducers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview of the J-ReCoVer Tool} \label{sec:overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{wrapfigure}{r}{7cm}
	\vspace{-3mm}
\centering
	\scalebox{0.7}{
		\begin{tikzpicture}

@@

		\end{tikzpicture}
	}
		\vspace{-1cm}
	\caption{Overview of the J-ReCoVer tool. }\label{fig:overview-jrecover}
		\vspace{-0.3cm}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Preprocessor and the Prover} \label{sec:preprocessor_prover}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%=============================================================================
\subsection{The Program Transformation in the Preprocessor}
\label{sec:program_trans1}
%=============================================================================

@@

\begin{wrapfigure}{r}{3.5cm}
	\vspace{-13mm}
	\begin{algorithm}[H]
		\;\;$m := \cur + 10$; \;
		\Loop{}{
			$t:=\cur$\;
			\uIf{ $t> m$}{
				$m := t$ \;
			}
		};
		$out(m)$\;\;
	\end{algorithm}

	\caption{The max$^+$ reducer with input before the main loop.}

	\label{fig:reducer_max1}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{5.3cm}

	\begin{algorithm}[H]
		$s:=1;$\;
		\Loop{}{
			\uIf{$s=1$}{$m := \cur + 10; s:= 2$}
			\uElse{
				$t:=\cur$\;
				\uIf{ $t > m$}{
					$m := t$ \;
				}
			}
		};
		$out(m)$
	\end{algorithm}	
	\vspace{-2mm}
	\caption{The max$^{+\mathtt{fix}}$ reducer.}
	\vspace{-4mm}
	\label{fig:reducer_max2}
\end{wrapfigure}

@@

%=============================================================================
\subsection{The Prover: Reduce Commutativity Checking to SMT Solving}
\label{sec:prover}
%=============================================================================

@@

The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$. The loop body $s_2$ contains no nested loop structure. Hence, a bounded summary in quantifier-free linear integer arithmetic is sufficient~for~describing~$F$.

Formally, the function $F(n,x_1,x_2,\ldots,x_k): \Z^{k+1}
\rightarrow \Z^k$ returns a tuple of values $x_1',x_2',\ldots,x_k'$ where $n$ is
the current input value of the reducer, $x_i$ and $x_i'$ are the values of the
variables before and after the execution of $s_2$, respectively, for
$i\in[1,k]$. The construction of $F$ from $s_2$ can be done in the standard way.

@@

%=============================================================================
\subsection{An Optimisation by Live Variable Analysis}
\label{section:optimizations}
%=============================================================================

@@

@@

\begin{wraptable}[7]{r}{40mm}

	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}

@@

%-----------------------------------------------------------------------------
\paragraph*{Benchmark collection} 
%-----------------------------------------------------------------------------

@@

%-----------------------------------------------------------------------------
\paragraph*{Results} 
%-----------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs-sorted}
\bibliography{refs}
